---
title: "R Project 1 - Hello R"
author: "Maxwell Boozer"
date: "9/16/2020"
output: 
  html_document: 
    fig_width: 8
    fig_height: 13
    highlight: zenburn
    theme: united
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns. The variables included in the data frame are "dataset, x, y"

### Exercise 2

Plotting the Dino dataset.

```{r plot-dino, fig.height=3, fig.width=4}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Determining the correlation coefficient for the Dino dataset.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the Star dataset.


```{r plot-star, fig.height=3, fig.width=4}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Determining the correlation coefficient for the Star dataset.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for the Star dataset is greater than that of the Dino dataset. 

### Exercise 4

Plotting the Circle dataset.

```{r plot-circle, fig.height=4, fig.width=4}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
Determining the correlation coefficient for the circle dataset.
 
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for the Circle dataset is less than that of the Dinosaur dataset.

### Exercise 5

Plotting all datasets within the dinosauRus package.

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```

Determining the correlation coefficient for all datasets within the dinosauRus package.

```{r cor-all}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```