---
title: "R Project 1 - Hello R"
author: "Maxwell Boozer"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows and 3 columns. The variables included in the data frame are "dataset, x, y"

### Exercise 2

Plotting the Dino dataset.

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Determining the correlation coefficient for the Dino dataset.

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the Star dataset.


```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Determining the correlation coefficient for the Star dataset.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for the Star dataset is greater than that of the Dino dataset. 

### Exercise 4

Plotting the Circle dataset.

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```
Determining the correlation coefficient for the circle dataset.
 
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
The correlation coefficient for the Circle dataset is less than that of the Dinosaur dataset.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)